\textbf{Species and genus plant classification with NEON hyperspectral remote sensing data}

### 2020-11-05 analysis/paper/paper.Rmd
results figures

Variable importance for species classification (Figure \@ref(fig:varImpSpecies))

@@

```{r fig-confMatSpecies, fig.cap ="Confusion matrix Species", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_species_valid.pdf"))
```

@@

```{r fig-confMatGenus, fig.cap ="Confusion matrix Genus", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_genus_valid.pdf"))
```

@@

```{r fig-varImpSpecies, fig.cap ="Variable Importance Species", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "varImp_species.pdf"))
```

>>>>

Variable importance for species classification (Figure \@ref(fig:fig-varImpSpecies))

@@

```{r fig-confMatSpecies, fig.cap ="Confusion matrix for species classification", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_species_valid.pdf"))
```

@@

```{r fig-confMatGenus, fig.cap ="Confusion matrix for genus classification", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "confMat_genus_valid.pdf"))
```

@@

```{r fig-varImpSpecies, fig.cap ="Variable importance for species classification", echo=FALSE,  out.width = "450px", message = FALSE, warning=FALSE}
library(here)
knitr::include_graphics(here::here("analysis","figures", "varImp_species.pdf"))
```
